# Methods and Analysis

```{r bibliometrix, echo=TRUE}
# install bibliometrix and load data
#install.packages("devtools")
#devtools::install_github("massimoaria/bibliometrix")
library(bibliometrix)
data <- readFiles("scopus.bib")
df <- convert2df(data, dbsource = "scopus",format = "bibtex")
```

## Descriptive analysis

### Primary findings related to the collection

```{r summary, echo=TRUE}
results <- biblioAnalysis(df, sep = ";")
options(width = 100)
s <- summary(object = results, k = 10, pause = FALSE)
plot(x = results, k = 10, pause = FALSE)
# calculate citations in the local network
CR <- localCitations(df, sep = ";")
# top 20 cited authors in local network
CR$Authors[1:10,]
# top 20 cited papers in local network
CR$Papers[1:10,]
# top authors' productivity over time
topAU <- authorProdOverTime(df, k = 10, graph = TRUE)
```

## Most cited references

```{r mostcitedrefs, echo=TRUE}
mcr <- citations(df, field = "article", sep = ";")
cbind(mcr$Cited[1:20])
```

## The intellectual structure of the field

### Article (references) co-citation

```{r refcocite, out.width = "100%", dpi = 300, echo=TRUE}
# article co-citation network
comat1 <- biblioNetwork(df, analysis = "co-citation", network = "references", sep = ";")
# network plot
conet1 = networkPlot(comat1, n = 50, Title = "Article Co-Citation Network", type = "auto", size = 20, size.cex = T, remove.multiple = FALSE, labelsize = 0.4, edgesize = 10, edges.min = 5)
# descriptive analysis of journal co-citation network
aconetstat <- networkStat(comat1)
summary(aconetstat, k = 15)
```

## Historiograph direct citation linkages

The historiographic map is a chronological network map of the most relevant direct citations resulting from this bibliographic collection.

```{r hdcn, out.width = "100%", dpi = 300, echo=TRUE}
# historical citation network
options(width = 100)
histResults <- histNetwork(df, min.citations = 4, sep = ";")
# plot historical co-citation network
hnet <- histPlot(histResults, n = 20, size = 8, labelsize = 4)
```

## The conceptual structure of the field

### Co-word analysis through keyword co-occurrences

```{r keywordco, out.width = "100%", dpi = 300, echo=TRUE}
# keyword co-occurrences network
keymat1 <- biblioNetwork(df, analysis = "co-occurrences", network = "keywords", sep = ";")
# networkplot
keynet1=networkPlot(keymat1, normalize = "association", weighted = T, n = 50, Title = "Keyword Co-occurrences", type = "fruchterman", size = T, edgesize = 5, labelsize = 0.7)
```

### Co-word analysis through Correspondence Analysis

Co-word analysis maps the conceptual structure of a research domain using the co-occurrence of words in the bibliiographic collection. This includes two analyses; the first using the author's keywords (DE), and the second using keywords plus (ID).

```{r coword1, out.width = "100%", dpi = 300, echo=TRUE}
# using authors keywords
cw <- conceptualStructure(df, field = "DE", method = "MCA", minDegree = 4, clust = 3, stemming = FALSE, labelsize = 5, documents = 97)
```

## Thematic mapping

```{r thematicmap, out.width = "100%", dpi = 300, echo=TRUE}
# keyword map
map1 = thematicMap(df, field = "ID", n = 97, minfreq = 2, stemming = FALSE, size = 0.8, n.labels = 4, repel = TRUE)
# plot map
plot(map1$map)
# abstract map
map2 = thematicMap(df, field = "AB", n = 97, minfreq = 5, stemming = FALSE, size = 0.8, n.labels = 4, repel = TRUE)
# plot map
plot(map2$map)
```

## Social structure - collaboration

### Author collaboration

Scientific collaborations are plotted where nodes are the authors and links are co-authorships.

```{r collab network, out.width = "100%", dpi = 300, echo=TRUE}
# author collaboration network
collab1 <- biblioNetwork(df, analysis = "collaboration", network = "authors", sep = ";")
# network plot
collabnet1 = networkPlot(collab1, n = 75, Title = "Author Collaboration", type = "auto", size = 15, size.cex = T, edgesize = 5, labelsize = 0.5)
# descriptive analysis of author collaboration network
collabnetstat <- networkStat(collab1)
summary(collabnetstat, k = 15)
```

### Edu collaboration

```{r edunetwork, out.width = "100%", dpi = 300, echo=TRUE}
# author collaboration network
educollab1 <- biblioNetwork(df, analysis = "collaboration", network = "universities",sep = ";")
# network plot
educollabnet1 = networkPlot(educollab1, n = 75, Title = "Edu Collaboration", type = "auto", size = 25, size.cex = T, edgesize = 5, labelsize = 0.5)
# descriptive analysis of edu collaboration network
edunetstat<-networkStat(educollab1)
summary(edunetstat, k = 15)
```

### Country collaboration

```{r countrycollab, out.width = "100%", dpi = 300, echo=TRUE}
# country collaboration network
count <- metaTagExtraction(df, Field = "AU_CO", sep = ";")
cmat1 <- biblioNetwork(count, analysis = "collaboration", network = "countries", sep = ";")
# network plot
cnet1 = networkPlot(cmat1, n = dim(cmat1)[1], Title = "Country Collaboration", type = "circle", size = 10, size.cex = T, edgesize = 3, labelsize = 0.6, cluster="none")
# descriptive analysis of country collaboration network
countnetstat <- networkStat(cmat1)
summary(countnetstat, k = 15)
#end of code
```

