# Methods and Analysis

```{r bibliometrix, echo=TRUE}
# install bibliometrix and load data
#install.packages("devtools")
#devtools::install_github("massimoaria/bibliometrix")
library(bibliometrix)
data<-readFiles("scopus.bib")
df<-convert2df(data, dbsource = "scopus",format = "bibtex")
```

## Descriptive summary

```{r summary, echo=TRUE}
results<-biblioAnalysis(df,sep = ";")
options(width = 100)
s<-summary(object = results, k = 10, pause = FALSE)
plot(x = results, k = 10, pause = FALSE)
# calculate citations in the local network
CR<-localCitations(df,sep = ";")
# top 20 cited authors in local network
CR$Authors[1:10,]
# top 20 cited papers in local network
CR$Papers[1:10,]
# top authors' productivity over time
topAU<-authorProdOverTime(df,k = 10, graph = TRUE)
```

## Bipartite networks

```{r network matrices, echo=TRUE}
pubnet<-cocMatrix(df,Field = "SO",sep = ";")
# identify 10 most relevant publication venues
sort(Matrix::colSums(pubnet),decreasing = TRUE)[1:10]
# compute citation network
citnet<-cocMatrix(df,Field = "CR", sep = ";")
# identify 10 most relevant citations
sort(Matrix::colSums(citnet),decreasing = TRUE)[1:10]
# compute author network
authnet<-cocMatrix(df,Field = "AU",sep = ";")
# identify 10 most relevant authors
sort(Matrix::colSums(authnet),decreasing = TRUE)[1:10]
# compute author-keyword network
aukeynet<-cocMatrix(df,Field = "DE",sep = ";")
# identify 10 most relevant keywords
sort(Matrix::colSums(aukeynet),decreasing = TRUE)[1:10]
```

## Author collaboration network

Scientific collaboration networks are plotted where nodes are the authors and links are co-authorships.

```{r collab network, echo=TRUE}
# author collaboration network
collab1<-biblioNetwork(df,analysis = "collaboration",network = "authors",sep = ";")
# network plot
collabnet1=networkPlot(collab1,weighted=TRUE,n = 200,Title = "Author Collaboration", type = "auto",curved = TRUE, size=5,size.cex=T,remove.multiple=TRUE, label = FALSE)
```

## Collaboration among countries

```{r countrycollab, echo=TRUE}
# country collaboration network
country <- metaTagExtraction(df, Field = "AU_CO", sep = ";")
cmat1 <- biblioNetwork(country, analysis = "collaboration", network = "countries", sep = ";")
# network plot
cnet1=networkPlot(cmat1, n = dim(cmat1)[1], Title = "Country Collaboration", type = "circle", size=TRUE, remove.multiple=FALSE,labelsize=0.7,cluster="none")
```

## Bibliographic coupling and co-citation

Bibliographic coupling occurs when two articles cite the same source. Bibliographic co-citation is a counterpart of bibliographic coupling, and co-citation occurs when two articles are cited in a third.

```{r network coupling, echo=TRUE}
# article coupling network
comat1<-biblioNetwork(df,analysis = "coupling",network = "references",sep = ";")
# network plot
conet1=networkPlot(comat1, weighted=TRUE, n = 500, Title = "Article Coupling", type = "auto",curved = TRUE, size=5,size.cex=T,remove.multiple=TRUE,labelsize=0.5,label.n=10,label.cex=F)
#article co-citation network
comat2<-biblioNetwork(df,analysis = "co-citation",network = "references",sep = ";")
# network plot
conet1=networkPlot(comat2, weighted=TRUE, n = 500, Title = "Article Co-Citation", type = "auto",curved = TRUE, size=5,size.cex=T,remove.multiple=TRUE,labelsize=0.5,label.n=10,label.cex=F)
```

## Keyword co-occurrence

```{r keywordco, echo=TRUE}
# keyword co-occurrences network
keymat1 <- biblioNetwork(df, analysis = "co-occurrences", network = "keywords", sep = ";")
# networkplot
keynet1=networkPlot(keymat1, normalize="association", weighted=T, n = 50, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```

## Co-word analysis

Co-word analysis maps the conceptual structure of a research domain using the co-occurrence of words in the bibliiographic collection.

```{r coword, echo=TRUE}
cw <- conceptualStructure(df,field="ID", method="CA", minDegree=4, clust=3, stemming=FALSE, labelsize=5, documents=25)
```

## Historical direct citation network

The historiographic map is a chronological network map of the most relevant direct citations resulting from this bibliographic collection.

```{r hdcn, echo=TRUE}
# historical citation network
options(width=100)
histResults <- histNetwork(df, min.citations = 4, sep = ";")
# plot historical co-citation network
hnet <- histPlot(histResults, n=15, size = 8, labelsize=4)
#end of code
```


