# Bibliometric Analysis

```{r bibliometrix, echo=TRUE, warning=FALSE}
# install bibliometrix and load data
#install.packages("devtools")
#devtools::install_github("massimoaria/bibliometrix")
library(bibliometrix)
library(reshape2)
library(ggplot2)
df <- convert2df(file = "scopus.bib", dbsource = "scopus",format = "bibtex")
```

## Descriptive analysis

### Attributes of the collection

```{r summary, echo=TRUE, warning=FALSE}
results <- biblioAnalysis(df, sep = ";")
options(width = 100)
s <- summary(object = results, k = 10, pause = FALSE)
# plot attributes
plot(x = results, k = 10, pause = FALSE)
```

### Attributes of the local network

```{r net.attr, echo=TRUE, warning=FALSE}
# calculate citations in the LOCAL network
CR <- localCitations(df, sep = ";")
# top 10 cited authors in LOCAL network
CR$Authors[1:10,]
# top 10 cited papers in LOCAL network
CR$Papers[1:10,]
# top authors' productivity over time
topAU <- authorProdOverTime(df, k = 10, graph = TRUE)
# number of documents published annually by top sources
topSO <- sourceGrowth(df, top = 10, cdf = TRUE)
topSO
# plot results
tso=melt(topSO, id = 'Year')
ggplot(tso, aes(Year, value, group = variable, color = variable)) + 
  geom_line()
```

### Three fields plot

```{r 3.flds, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Interactive visualization of three fields (authors, keywords, and journals) illustrating how they are related."}
threeFieldsPlot(df, fields = c("AU", "DE", "SO"), n = c(20,20,20))
```

## Most cited

### Most cited articles

```{r mostcitedrefs, echo=TRUE, warning=FALSE}
# most cited references in global network
mcr <- citations(df, field = "article", sep = ";")
cbind(mcr$Cited[1:20])
```

### Most cited authors

```{r mostcitedauths, echo=TRUE, warning=FALSE}
# most cited authors in global network
mcr <- citations(df, field = "author", sep = ";")
cbind(mcr$Cited[1:20])
```

## The intellectual structure of the field

### Reference co-citation

```{r refcocite, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# article co-citation network
comat1 <- biblioNetwork(df, analysis = "co-citation", network = "references", sep = ";")
# network plot
conet1 = networkPlot(comat1, n = 50, Title = "Reference Co-Citation Network", type = "auto", size = 20, size.cex = T, remove.multiple = FALSE, labelsize = 0.4, edgesize = 5, edges.min = 3)
# descriptive analysis of journal co-citation network
aconetstat <- networkStat(comat1)
summary(aconetstat, k = 15)
```

## Historiograph direct citation linkages

```{r hdcn, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="The historiographic map is a chronological network map of the most relevant direct citations resulting from this bibliographic collection."}
# historical citation network
options(width = 100)
histResults <- histNetwork(df, min.citations = 5, sep = ";")
# plot historical co-citation network
hnet <- histPlot(histResults, n = 50, size = 4, labelsize = 2)
```

## The conceptual structure of the field

### Co-word analysis through keyword co-occurrences

```{r keywordco, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# keyword co-occurrences network
keymat1 <- biblioNetwork(df, analysis = "co-occurrences", network = "keywords", sep = ";")
# networkplot
keynet1=networkPlot(keymat1, normalize = "association", n = 50, Title = "Keyword Co-occurrences", type = "auto", size = 5, edgesize = 2, labelsize = 0.4)
```

### Co-word analysis through Multiple Correspondence Analysis

```{r coword1, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Co-word analysis was used to map the conceptual structure of the research domain using co-occurrence of keywords in the bibliographic collection."}
# using authors keywords
cw <- conceptualStructure(df, field = "DE", method = "MCA", minDegree = 3, clust = "auto", stemming = FALSE, labelsize = 8, documents = 15)
```

## Thematic mapping

```{r thematicmap, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Thematic maps are intuitive plots that can be analyzed according to the quadrant in which the theme occurs. The top right quadrant articulates with motor themes, the bottom right with basic and transversal themes, the lower left with emerging or declining themes, and the upper left with highly developed and isolated themes (Cobo et al. 2011)."}
# keyword map
map1 = thematicMap(df, field = "DE", n = 1000, minfreq = 3, stemming = FALSE, size = 0.8, n.labels = 1, repel = TRUE)
# plot map
plot(map1$map)
```

### Thematic evolution

```{r thematicevol, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# keyword thematic evolution
nexus <- thematicEvolution(df, field = "DE", years = c(2010,2015), n = 1000, minFreq = 2, size = 0.8, n.labels = 1, repel = TRUE)
nexus
```

## Social structure - collaboration

### Author collaboration

```{r collab.network, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="In this figure, scientific collaborations are plotted where nodes are authors and links are co-authorships, illustrating collaborations between authors."}
# author collaboration network
collab1 <- biblioNetwork(df, analysis = "collaboration", network = "authors", sep = ";")
# network plot
collabnet1 = networkPlot(collab1, n = 100, Title = "Author Collaboration", type = "auto", size = 15, size.cex = T, edgesize = 3, labelsize = 0.5)
# descriptive analysis of author collaboration network
collabnetstat <- networkStat(collab1)
summary(collabnetstat, k = 15)
```

### Edu collaboration

```{r edu.collab, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="In this figure, scientific collaborations are plotted where nodes are institutions and links are co-authorships, illustrating collaborations between institutions."}
# author collaboration network
educollab1 <- biblioNetwork(df, analysis = "collaboration", network = "universities",sep = ";")
# network plot
educollabnet1 = networkPlot(educollab1, n = 50, Title = "Edu Collaboration", type = "fruchterman", size = 25, size.cex = T, edgesize = 3, labelsize = 0.4)
# descriptive analysis of edu collaboration network
edunetstat<-networkStat(educollab1)
summary(edunetstat, k = 15)
```

### Country collaboration

```{r country.collab, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="In this figure, scientific collaborations are plotted where nodes are countries and links are co-authorships, illustrating collaborations between countries"}
# country collaboration network
count <- metaTagExtraction(df, Field = "AU_CO", sep = ";")
cmat1 <- biblioNetwork(count, analysis = "collaboration", network = "countries", sep = ";")
# network plot
cnet1 = networkPlot(cmat1, n = dim(cmat1)[1], Title = "Country Collaboration", type = "circle", size = 10, size.cex = T, edgesize = 1, labelsize = 0.6, cluster = "none")
# descriptive analysis of country collaboration network
countnetstat <- networkStat(cmat1)
summary(countnetstat, k = 15)
#end of code
```

